---
title: "Fish"
author: "Barbara Rose Hoover"
date: "2/14/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, messages = FALSE}
library(tidyverse)
library(boot)
library(simputation)
```

# Task 2: Parameter Estimation – Wild Fish Catch

```{r data, message=FALSE, warning = FALSE}
fish <- read_csv("fish_catch.csv") #read in csv
```

```{r data wrangling, message=FALSE, warning = FALSE}
fish_df <- fish %>% #wrangling to remove unnecessary rows and rename columns
  setNames(.,(c("year","wild","farmed","total"))) %>% 
  slice(5:67)  

fish_df$wild<-as.integer(fish_df$wild)
fish_df$year<-as.integer(fish_df$year)
fish_df<-mutate(fish_df, number = year - 1950)


```

## a) Exploratory Plot
```{r plot, message=FALSE, warning = FALSE}
#exploratory plot 
ggplot(fish_df, aes(x = year, y=wild))+
  geom_point()+
  ylim(15,95)
```

## b) Logistic growth  

Logistic growth equation: N(t) = A/(1+Be^-rt)

Estimate for K/A: ~ 90
Estimate for N0: ~ 15
Estimate for B: ~ 5
  BEstimate <- (90 - 15)/15 # BEstimate = 5



```{r estimate_r, message=FALSE, warning = FALSE}
#finding slope of line to get 'r' (growth rate constant)
r_fish_est <- lm(log(fish_df$wild[1:5]) ~ fish_df$number[1:5]) #r=0.07046
```

$N_t = \left(\frac{A}{1 + \beta e^{-rt}}\right)$  

Carrying Capacity (A) from the exploratory graph above:  
A = 90 million tons

If $N_0 = 15$ million tons estimate $\beta$:  
  
$\beta = \frac{(K - N_0)}{N_0}$   
  
$\beta = \frac{(90-15)}{15} = 5$ million tons 

```{r model fitting, message=FALSE, warning=FALSE}
fish_fit<- nls(wild ~ A/(1+B*exp(-r*number)), 
        start = list(A = 90, B = 5, r = 0.0705), 
        data = fish_df, trace = TRUE) 
```

```{r storing code, include=FALSE}
#storing code for final graph
A <- coef(fish_fit)[1]
B <- coef(fish_fit)[2]
r <- coef(fish_fit)[3]
```

## c) Parameters:  
 
$A = 99.8$ million tons   

 
$\beta =  4.38$ million tons      

 
$r = 0.0705$ million tons per year   

## d) Finalized Graph: 

```{r final graph, message=FALSE, warning=FALSE}
# Create a new sequence containing a series of times over which fish caught is predicted 
time_seq <- seq(0,65, length=100) 
#Using the parameters (A, B, and r) and the time sequence to predict the fish caught for the logistic growth model
fish_pred <- A/(1+B*exp(-r*time_seq))
#  Bind together the time sequence data and the predictions data into a new data frame
pred_df <- data.frame(time_seq, fish_pred)
#Final graph showing the original data (as scatterplot points) and the predicted data (as a line graph) 
ggplot(fish_df, aes(x = number, y = wild)) +
  geom_point(color = "gray", size = 2, alpha = 0.7) +
  geom_line(data = pred_df, aes(x = time_seq, y = fish_pred), color = "blue", size = 1) + 
  scale_x_continuous(expand = c(0,0.5), limits = c(0,70), breaks = seq(0,70, by = 10)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,100)) +
  labs(x = "Time \n(Years since 1950)", y = "Wild Fish Catch \n(Million Tons)") +
  theme_bw() 
```

#Task 3: Bootstrapped Confidence Interval for Proportions


## a) Original Sample Vector:

```{r bootstrap, warning=FALSE, message=FALSE}
# Find a confidence interval for the proportion of nonbinary/genderqueer students experiencing exclusionary, hostile or intimidating experience at UCSB.

# Original data from survey (n = 36): 22 indicated they experienced exclusionary conduct 

# Create a vector of proportions to use for bootstrapping: 
survey <- c(rep.int(1, 22), rep.int(0, 14)) # 0 = did not experience exclusionary conduct, 1 = did experience exclusionary conduct 

# # Create a function to calculate the mean of varying vectors (x) of index (i)
mean_fun <- function(x,i) {mean(x[i])}
# Bootstrapping with 10,000:
boot_10000<-boot(survey, mean_fun, R=10000)
# Bootstrap with 100,000:
boot_100000<-boot(survey, mean_fun, R=100000)
#Shows decrease in bias. Little change in standard error
```

## b) Histogram of Boostrapped Proportions:

```{r histogram, message=FALSE, warning = FALSE}
bin <- 2*((NROW(boot_100000$t))^(1/3))
ggplot() +
  aes(boot_100000$t) +
  geom_histogram(bins = bin) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0), limits = c(0,15000)) +
  theme_bw()
```

## c) Confidence Interval: 

```{r boostrap CI, include=FALSE}
boostrap_ci <- boot.ci(boot_100000, conf = 0.95)
# Percentile CI (0.452, 0.7771)
```

The proportion of UCSB students identifying as nonbinary/genderqueer who experience exclusionary, hostile, or intimidating conduct is [0.452, 0.777] with a 95% confidence interval (n = 100,000 bootstrap samples).  
